---
title: "Exercícios Aula 6"
author: "Caio César Albuquerque"
date: "2022-10-05"
output:
  html_document:
    df_print: paged
---
###Function "po()" -> pipe operator, makes it possible to try several different pre-processing methods, assessment parameters and algorithms at the same time. Pipeline operators are building blocks to compose linear machine learning pipelines.


```{r}
library(earth)
library(tidyverse)
library(mlr3verse)
library(igraph)
library(mlr3extralearners)
library(rpart) # para arvore de decisao
```


```{r}
link <- "https://raw.githubusercontent.com/jacobwright32/Web_Scraper_AI_Core_Project/bb4865ae568e23ab8fadb6ea58cf117df2164ef3/web%20scraping/Cleaned%20Data/Brazil_Sao%20Bernardo%20Do%20Campo_Cleaned.csv"
dados <- readr::read_csv(link)
```

### Crie três diferentes pré-processamentos para as features numéricas da base. As pipelines devem usar regressão linear simples como modelo para predizer a variável "maximum_temprature".
```{r}
dados <- dados %>% 
  select_if(is.numeric)

# Creating the pipelines (gr) without transforming the data, just including a linear model.
gr <- po("learner", learner = lrn("regr.lm")) %>% 
  as_learner() # turns the pipeline into a learner
# gr (graphos) is a common name for pipelines

# Pipeline that standardizes the variables
gr2 <- po("scale") %>>% 
  po("learner", learner = lrn("regr.lm")) %>% 
  as_learner()

gr2$graph$plot() # view the grapho


# Pipeline including some polynomials
gr3 <- po("scale") %>>% 
  po("mutate") %>>% 
  po("learner", learner = lrn("regr.lm")) %>% 
  as_learner()
 
gr3$param_set$values$mutate.mutation <- list(
  teste = ~ cloud_coverage^2,
  teste2= ~ cloud_coverage^3,
  teste3 = ~ pressure^2,
  teste4 = ~ pressure^3,
  teste5 = ~ humidity^2,
  teste6 = ~ humidity^3,
  teste7 = ~ amount_of_rain^2,
  teste8 = ~ amount_of_rain^3
)

# Polynomial pipeline - KNN
gr4 <- po("scale") %>>% 
  po("mutate") %>>% 
  po("learner", learner = lrn("regr.kknn")) %>% 
  as_learner()
 
gr4$param_set$values$mutate.mutation <- list(
  teste = ~ cloud_coverage^2,
  teste2 = ~ cloud_coverage^3,
  teste3 = ~ pressure^2,
  teste4 = ~ pressure^3,
  teste5 = ~ humidity^2,
  teste6 = ~ humidity^3,
  teste7 = ~ amount_of_rain^2,
  teste8 = ~ amount_of_rain^3
)

# MARS - Multivariate Adaptive Regression Splines
gr5 <- po("scale") %>>%
  po("mutate") %>>%
  po("learner", learner = lrn("regr.earth")) %>% 
  as_learner()

# TREE
gr6 <- po("scale") %>>%
  po("mutate") %>>%
  po("learner", learner = lrn("regr.rpart")) %>% 
  as_learner()

# The pipelines are independent from the tasks



# Training the pipeline
roda_benchmark <- function() {
  design <- benchmark_grid(
  tasks = as_task_regr(maximum_temprature ~ ., data = dados),
  learners = list(gr, gr2, gr3, gr4, gr5, gr6),
  resampling = rsmp("holdout", ratio = 0.7)
)

results <- benchmark(design)
results$score(msr("regr.rmse"))
}

roda_benchmark()
```


### Aplicar o modelo com os melhores preditores nos dados de Campinas (gr3 e gr5)
```{r}
campinas <- "https://raw.githubusercontent.com/jacobwright32/Web_Scraper_AI_Core_Project/bb4865ae568e23ab8fadb6ea58cf117df2164ef3/web%20scraping/Cleaned%20Data/Brazil_Sao%20Bernardo%20Do%20Campo_Cleaned.csv"
campinas <- readr::read_csv(campinas)

campinas <- campinas %>% 
  select_if(is.numeric)

roda_benchmark2 <- function(){
  design <- benchmark_grid(
  tasks = as_task_regr(maximum_temprature ~ ., data = campinas),
  learners = list(gr3, gr5),
  resampling = rsmp("holdout", ratio = 0.7)
)
  
results2 <- benchmark(design)
results2$score(msr("regr.rmse"))
}

roda_benchmark2()
```

### Run previous function 100x
```{r}
results2 <- 1:100 %>% 
  map_df(~ roda_benchmark2())

results2 %>% 
  ggplot(aes(group = nr, y = regr.rmse)) + # it's important to check the data results to select the variables 
  geom_boxplot()
```

### Aplicar o modelo em novos dados - Clima em Southampton
```{r}
southampton <- "https://raw.githubusercontent.com/jacobwright32/Web_Scraper_AI_Core_Project/master/web%20scraping/Cleaned%20Data/United%20Kingdom_Southampton_Cleaned.csv"
southampton <- readr::read_csv(southampton)

southampton <- southampton %>% 
  select_if(is.numeric)

roda_benchmark3 <- function(){
  design <- benchmark_grid(
  tasks = as_task_regr(maximum_temprature ~ ., data = southampton),
  learners = list(gr3, gr5),
  resampling = rsmp("holdout", ratio = 0.7)
)
  
results3 <- benchmark(design)
results3$score(msr("regr.rmse"))
}

roda_benchmark3()
```

### Run previous function 100x
```{r}
results3 <- 1:100 %>% 
  map_df(~ roda_benchmark3())

results3 %>% 
  ggplot(aes(group = nr, y = regr.rmse)) + # it's important to check the data results to select the variables 
  geom_boxplot()
```



### Exercicio 2
```{r}
library(quanteda)
library(tidytext)
# pesquisar argumentos para tokenization do quanteda --> ?quanteda::tokens
```

```{r}
link <- "https://github.com/FLS-6497/datasets/raw/main/aula5/discursos_presidenciais.csv"
discursos <- readr::read_csv2(link) 
```


```{r}
tsk <- as_task_classif(planalto ~ discurso, data = discursos)

# Pipeline - Naive Bayes
gr_bow1 <- po("textvectorizer", param_vals = list(stopwords_language = "pt"), remove_punct = TRUE, remove_numbers = TRUE, remove_symbols = TRUE, min_termfreq = 20) %>>%
  po("learner", learner = lrn("classif.naive_bayes")) %>% 
  as_learner()
 
# Pipeline - Naive Bayes (n-gram = 2)
gr_bow2 <- po("textvectorizer", param_vals = list(stopwords_language = "pt"), remove_punct = TRUE, remove_numbers = TRUE, remove_symbols = TRUE, min_termfreq = 20, n = 2) %>>%
  po("learner", learner = lrn("classif.naive_bayes")) %>% 
  as_learner()

# Pipeline - Decision Tree 
gr_bow3 <- po("textvectorizer", param_vals = list(stopwords_language = "pt"), remove_punct = TRUE, remove_numbers = TRUE, remove_symbols = TRUE, min_termfreq = 20) %>>%
  po("learner", learner = lrn("classif.rpart")) %>% 
  as_learner()

# Pipeline - Decision Tree (n-gram = 2)
gr_bow4 <- po("textvectorizer", param_vals = list(stopwords_language = "pt"), remove_punct = TRUE, remove_numbers = TRUE, remove_symbols = TRUE, min_termfreq = 20, n = 2) %>>%
  po("learner", learner = lrn("classif.rpart")) %>% 
  as_learner()

# Execute the pipelines as learners
bench <- function(){
design <- benchmark_grid(
  tasks = tsk,
  learners = list(gr_bow1, gr_bow2, gr_bow3, gr_bow4),
  resampling = rsmp("holdout", ratio = 0.7)
)
resultados <- benchmark(design)
resultados$score(msr("classif.fbeta"))
}

bench()

play_function <- 1:10 %>% 
  map_df(~ bench())

# Boxplot
play_function %>% 
  ggplot(aes(group = nr, y = classif.fbeta)) + geom_boxplot()
```

